---
title: "References"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2: 
    toc: FALSE
    toc_float: TRUE
link-citations: yes
fontsize: 12pt
urlcolor: blue
csl: AmJBot.csl
bibliography: References.bib
editor_options: 
  markdown: 
    wrap: sentence
---

```{r packages, echo=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(rmarkdown)
library(bookdown)
#library(distill)
library(knitcitations)
library(formatR)
library(devtools)
library(kfigr)
library(dplyr)
library(kableExtra)

#Generate BibTex citation file for all R packages used to produce report
#knitr::write_bib(.packages(), file = 'packages.bib')
```

References used in the BIOL 497/597 - Genomics & Bioinformatics course are cited here. The citation of references supports transparency in science as well as provides opportunities for students to further their knowledge by accessing articles and books used to develop this course. The `BibTex` document is accessible [here](References.bib). Please contact the instructor (svenbuerki@boisestate.edu) to add missing references to this document.

```{r references, eval = T, results="asis", cache = F, echo=F, warning = FALSE, message=FALSE}
library("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "References.bib")
``` 
