---
title: "References"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2: 
    toc: FALSE
    toc_float: TRUE
link-citations: yes
fontsize: 12pt
urlcolor: blue
csl: AmJBot.csl
bibliography: References.bib
editor_options: 
  markdown: 
    wrap: sentence
---

```{r packages, echo=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(rmarkdown)
library(bookdown)
#library(distill)
library(knitcitations)
library(formatR)
library(devtools)
library(kfigr)
library(dplyr)
library(kableExtra)

#Generate BibTex citation file for all R packages used to produce report
#knitr::write_bib(.packages(), file = 'packages.bib')
```

References (web resources and publications) used in the BIOL 497/597 - Genomics & Bioinformatics course are cited here. The citation of references supports transparency in science as well as provides opportunities for students to further their knowledge by accessing articles and books used to develop this course. The `BibTex` document is accessible [here](References.bib). Please contact the instructor (svenbuerki@boisestate.edu) to add missing references to this document.

# Web resources

- **Human Genome Project**: This [webpage](https://www.nature.com/scitable/topicpage/dna-sequencing-technologies-key-to-the-human-828/) contain details on the human genome project, especially associated to the applied sequencing strategy.
- **An Overview of Next-Generation Sequencing**: This [webpage](https://www.technologynetworks.com/genomics/articles/an-overview-of-next-generation-sequencing-346532) contains information related to next-generation sequencing. 
- **The Earth BioGenome Project**: A [special issue](https://www.pnas.org/cc/the-earth-biogenome-project) published in *PNAS* with a collection of articles on this project.

# Publications

```{r references, eval = T, results="asis", cache = F, echo=F, warning = FALSE, message=FALSE}
library("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "References.bib")
``` 
