---
title: "Schedule"
date: "`r Sys.Date()`"
output:
#  bookdown::pdf_document2:
#    toc: FALSE
  bookdown::html_document2: 
    toc: TRUE
    toc_float: TRUE
link-citations: yes
fontsize: 12pt
urlcolor: blue
csl: AmJBot.csl
bibliography: References.bib
editor_options: 
  markdown: 
    wrap: sentence
---

```{js logo-js, echo=FALSE}
$(document).ready(function() {
  $('#header').parent().prepend('<div id=\"logo\"><img src=\"Images/boisestate-primarylogo-2color-rgb.png\" style=\"position:absolute; top:4; right:0; padding:10px; height:120px\"></div>');
  $('#header').css('margin-right', '120px')
});
```

```{r packages, echo=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(rmarkdown)
library(bookdown)
#library(distill)
library(knitcitations)
library(formatR)
library(devtools)
library(kfigr)
library(dplyr)
library(kableExtra)
library(tufte)

#Generate BibTex citation file for all R packages used to produce report
knitr::write_bib(.packages(), file = 'packages.bib')
```


# Course Information Hub

Welcome to the central hub for course organization in **BIOL 497/597 – Genomics & Bioinformatics**. This webpage consolidates all essential information related to **assignment deadlines**, the **weekly schedule**, and the **typical structure of class meetings**.  

Here you will find:  

- [**Assignment Deadlines:**](#ass) Dates and point allocations for graded work, along with submission instructions.
- [**Tentative Weekly Schedule:**](#schedule) Topics, activities, and milestones for each class session.  
- [**Class Structure:**](#classstr) Overview of how lectures, laboratory exercises, and group activities are integrated throughout the semester.  

This page serves as a single reference point to help you plan your semester, stay on top of coursework, and engage fully with both theoretical and applied aspects of genomics and bioinformatics.

# Assignment Deadlines {#ass}

To facilitate communication, **deadlines** and **point allocations** for all course assignments are provided in Table \@ref(tab:deadlines).  

For more detailed information on each assignment, please see [Assessments and Grading](https://svenbuerki.github.io/Genomics-Bioinformatics/index.html#12_Assessments_and_Grading).  

All assignments must be submitted via [Google Drive](https://drive.google.com/drive/folders/1BFZFJeR8tW8N7QLfngqIVbjqEkDuIyWj?usp=sharing).

```{r deadlines, echo=FALSE}
###~~~
# Load data
###~~~
deadlines <- data.frame(read.csv("Data/deadlines.csv"))

# Convert to Date class and then format as "YYYY-MM-DD"
deadlines$Date <- format(as.Date(deadlines$Date, format = "%m/%d/%y"), "%Y-%m-%d")

###~~~
#Plot deadlines in doc
###~~~
knitr::kable(deadlines,  caption = "Deadlines of graded assignments for Genomics and Bioinformatics, Spring 2026 semester.", format = "html", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

<div class="info">
  <p><strong>💡 Information</strong></p>
  <ul>
    <li>Extra credit assignments will be announced later in the semester. Deadlines will be posted here.</li>
  </ul>
</div>

# Schedule {#schedule}

The tentative schedule for this course is provided in Table \@ref(tab:timetab). Please note that the instructor may adjust our schedule to accommodate the course’s progress and students’ needs. Any changes will be communicated to enrolled students in a timely manner.

```{r timetab, echo=FALSE}
###~~~
# Build a data frame with all dates from beginning to end of Fall semester
###~~~
dates <- data.frame(seq.Date(from=as.Date("2026/01/12"), to=as.Date("2026/05/01"), by="day"))
#Assign a name to the col (allows using $)
colnames(dates) <- "Date"

###~~~
# Find weekdays associated to dates
###~~~
#Add a col to dataframe with weekday
dates$Weekday <- weekdays(dates$Date)

###~~~
# Classes only take place on Wed and Fri. So, extract dates matching class weekdays
###~~~
#Subset dates based on selected weekdays
datesclass <- subset(dates, dates$Weekday %in% c("Wednesday"))

###~~~
# Add week ID (from 1 to 16) to object from step 4
###~~~
#Create weekID vector and add it in front of dataframe
datesclass <- data.frame(WeekID = sort(rep(seq(from=1, to=16, by=1), 1)), datesclass)

###~~~
# Exclude dates falling during holiday break
###~~~
#Establish vector of dates related to holidays
holiday <- seq.Date(from=as.Date("2026/03/16"), to=as.Date("2026/03/20"), by="day")

#Find and exclude holidays
datesclass <- datesclass[-which(datesclass$Date %in% holiday),]

###~~~
#Read in csv with topics and tasks
###~~~
topic <- read.csv("Data/topics_classes_2026.csv") 
topic <- as.data.frame(topic)

###~~~
#Produce final timetable
###~~~
timetable <- data.frame(datesclass, topic)

###~~~
#Plot timetable in doc
###~~~
knitr::kable(timetable,  caption = "Tentative schedule for Genomics and Bioinformatics, Spring 2026 semester.", format = "html", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
#PDF
#landscape(knitr::kable(timetable, caption = "Tentative timetable for the Spring semester 2023.", booktabs = T) 
#                       %>% kable_styling(latex_options = c("striped","scale_down"))
#)
```

# Class Structure {#classstr}

The weekly class structure is summarized in Table \@ref(tab:classstr).

A typical class meeting is structured as follows:

- An initial **lecture component** (ca. 50 minutes) introducing key concepts and methods  
- A brief **break and transition period**  
- A **laboratory session** (ca. 1 hour 40 minutes), which may include group activities, guided exercises, or computer-based data analysis 

During the **first several weeks of the semester**, class time will emphasize lectures and structured group activities to build foundational knowledge and skills. As the semester progresses, the course will gradually transition to **primarily computer-based laboratory work**, with increased emphasis on independent and applied problem-solving.

```{r classstr, echo=FALSE, warning = F, message = F}
###~~~
# Read in csv with weekly class structure, prevent R from changing names
class <- read.csv("Data/Class_structure.csv", check.names = FALSE) 
class <- as.data.frame(class)

###~~~
# Update column names for columns 2 to 4 to display times nicely
colnames(class)[2:4] <- c("9:00–9:50 a.m.", "9:50–10:05 a.m.", "10:05–11:45 a.m.")

###~~~
# Plot timetable in document
knitr::kable(class, 
             caption = "Weekly class structure for Genomics and Bioinformatics, Spring 2026 semester.", 
             format = "html", 
             row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

