---
title: "Schedule"
date: "`r Sys.Date()`"
output:
#  bookdown::pdf_document2:
#    toc: FALSE
  bookdown::html_document2: 
    toc: TRUE
    toc_float: TRUE
link-citations: yes
fontsize: 12pt
urlcolor: blue
csl: AmJBot.csl
bibliography: References.bib
editor_options: 
  markdown: 
    wrap: sentence
---

```{js logo-js, echo=FALSE}
$(document).ready(function() {
  $('#header').parent().prepend('<div id=\"logo\"><img src=\"Images/boisestate-primarylogo-2color-rgb.png\" style=\"position:absolute; top:4; right:0; padding:10px; height:120px\"></div>');
  $('#header').css('margin-right', '120px')
});
```

```{r packages, echo=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(rmarkdown)
library(bookdown)
#library(distill)
library(knitcitations)
library(formatR)
library(devtools)
library(kfigr)
library(dplyr)
library(kableExtra)
library(tufte)

#Generate BibTex citation file for all R packages used to produce report
knitr::write_bib(.packages(), file = 'packages.bib')
```

# Assignment Deadlines

To facilitate communication, **deadlines** and **point allocations** for all course assignments are provided in Table \@ref(tab:deadlines).  

For more detailed information on each assignment, please see [Assessments and Grading](https://svenbuerki.github.io/Genomics-Bioinformatics/index.html#12_Assessments_and_Grading).  

All assignments must be submitted via [Google Drive](https://drive.google.com/drive/folders/1BFZFJeR8tW8N7QLfngqIVbjqEkDuIyWj?usp=sharing).

```{r deadlines, echo=FALSE}
###~~~
# Load data
###~~~
deadlines <- data.frame(read.csv("Data/deadlines.csv"))

# Convert to Date class and then format as "YYYY-MM-DD"
deadlines$Date <- format(as.Date(deadlines$Date, format = "%m/%d/%y"), "%Y-%m-%d")

###~~~
#Plot deadlines in doc
###~~~
knitr::kable(deadlines,  caption = "Deadlines of graded assignments for Genomics and Bioinformatics, Spring 2026 semester.", format = "html", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# Schedule

The tentative schedule for this course is provided in Table \@ref(tab:timetab). Please note that the instructor may adjust our schedule to accommodate the course’s progress and students’ needs. Any changes will be communicated to enrolled students in a timely manner.

```{r timetab, echo=FALSE}
###~~~
# Build a data frame with all dates from beginning to end of Fall semester
###~~~
dates <- data.frame(seq.Date(from=as.Date("2026/01/12"), to=as.Date("2026/05/01"), by="day"))
#Assign a name to the col (allows using $)
colnames(dates) <- "Date"

###~~~
# Find weekdays associated to dates
###~~~
#Add a col to dataframe with weekday
dates$Weekday <- weekdays(dates$Date)

###~~~
# Classes only take place on Wed and Fri. So, extract dates matching class weekdays
###~~~
#Subset dates based on selected weekdays
datesclass <- subset(dates, dates$Weekday %in% c("Wednesday"))

###~~~
# Add week ID (from 1 to 16) to object from step 4
###~~~
#Create weekID vector and add it in front of dataframe
datesclass <- data.frame(WeekID = sort(rep(seq(from=1, to=16, by=1), 1)), datesclass)

###~~~
# Exclude dates falling during holiday break
###~~~
#Establish vector of dates related to holidays
holiday <- seq.Date(from=as.Date("2026/03/16"), to=as.Date("2026/03/20"), by="day")

#Find and exclude holidays
datesclass <- datesclass[-which(datesclass$Date %in% holiday),]

###~~~
#Read in csv with topics and tasks
###~~~
topic <- read.csv("Data/topics_classes_2026.csv") 
topic <- as.data.frame(topic)

###~~~
#Produce final timetable
###~~~
timetable <- data.frame(datesclass, topic)

###~~~
#Plot timetable in doc
###~~~
knitr::kable(timetable,  caption = "Tentative schedule for Genomics and Bioinformatics, Spring 2026 semester.", format = "html", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
#PDF
#landscape(knitr::kable(timetable, caption = "Tentative timetable for the Spring semester 2023.", booktabs = T) 
#                       %>% kable_styling(latex_options = c("striped","scale_down"))
#)
```


